04_DESeq_sexes_manipulate

### 2019-09-07 analysis/04_DESeq2_sexes_manipulate.Rmd
figure titles
eh

```{r wgcna, eval = T}
plotWGCNAcandidatesManip(vsd.pit, c("NP_990797.2", "NP_001090992.1", "NP_990136.1", "NP_001035179.1"), colDataPit, "PRL, VIPR1, TH & AR expression, Pituitary")

@@

prl36 <-  PRL_manipulated$entrezid[252:271]
plotWGCNAcandidatesManip(vsd.pit, prl36, colDataPit, "A-K genes with PRL pattern in the pituitary")

>>>>

```{r wgcna, eval = T, echo = F}
plotWGCNAcandidatesManip(vsd.pit, c("NP_990797.2", "NP_001090992.1", "NP_990136.1", "NP_001035179.1"), colDataPit, "PRL, VIPR1, TH & AR expression, Pituitary")

@@

prl36 <-  PRL_manipulated$entrezid[252:271]
plotWGCNAcandidatesManip(vsd.pit, prl36, colDataPit, "PRL-RIPK3 pattern in the PRL module")
```
